Model Comparisons

### 2015-11-20 models/Model_Comparison.Rmd
added by star and by scale correlation plots

m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
  geom_point(aes(colour = scale)) +
  geom_smooth(method=lm) +
  ggtitle("Model performance: M3 fit") +
  labs(x = "human judgments", y="model prediction")

m3.matched.fit.CorPlot
```

>>>>

# Full model fitted - color scale
m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
  geom_point(aes(colour = scale)) +
  geom_smooth(method=lm) +
  ggtitle("Model performance: M3 fit") +
  labs(x = "human judgments", y="model prediction")
m3.matched.fit.CorPlot

# Full model fitted - color stars
m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
  geom_point(aes(colour = stars)) +
  geom_smooth(method=lm) +
  ggtitle("Model performance: M3 fit") +
  labs(x = "human judgments", y="model prediction")
m3.matched.fit.CorPlot
```
